\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Steven An}

\section{Work experience}

\begin{eventlist}

\item{May 2017 -- August 2017}
     {Computer Engineering Internship}
     {Radial Electronics}

Conducted tests of different capacitive soil moisture sensors. Used
data to design a schematic and PCB layout for a proprietary sensor for
Radial E. Soldered and tested working circuits. Worked lightly with LORA,
a wireless communication protocol to communicate between sensor
and a raspberry pi “gateway”.

\item{March 2016 -- February 2017}
     {Engineering Architect}
     {Sacramento County DWMR}

Assisted the senior civil engineer in writing and modifying reports
submitted to the United States Environmental Protection Agency
(EPA). Coded a program to automate complex instructions and
calculations in C++.

\item{December 2015 -- March 2016}
     {Student Engineer}
     {State of California - Legislative Data Center}

Working with a team of other student interns, managed a large
database of legislative information for Sacramento City Hall. Routinely
checked on servers and tape archive machines. Ran server checks
and tests on proprietary mainframe. Maintained and debugged servers
through a Linux command line.


\end{eventlist}



\section{Education}

\begin{yearlist}

\item[2015-2018 Computer Engineering B.S]{}
     {California State University, Sacramento}
     {Sacramento, California}

\item[2012-2015]{}
      {De Anza Community College}
      {Cupertino, California}


\item[2011-2012 Computer Engineering B.S (not completed)]{}
     {University of California, Davis}
     {Davis, California}

\item[2007-2011 High school diploma]{}
     {The King's Academy College Prepatory}
     {Sunnyvale, California}



\end{yearlist}

\personal
    [www.stevenan.com]
    {3075 Redding Ave\newline Sacramento, California 95820}
    {(408) 600 - 8254}
    {steven.an93@gmail.com}

\section{Public projects}

\begin{yearlist}

\item{}
     {LoRa IoT Irrigation Sensor}
     {Design and implemented a custom PCB circuit that measured temperature, soil moisture, methane and ph levels and sent that data using the LoRa protocol to a cloud connected gateway for user monitoring}
     
\item{} 
     {Attendance Tracker}
     {Wrote and debugged code that communicated with Google API services to manage a database of names and attendance
     dates for a program that would track student attendance automatically, saving precious class time. Employed several different software engineering techniques including documentation and version control.}

\item{}
    {Contour Map Generator}
    {Wrote a C++ program when working at DWMR that took data from user input and performed complex generated a data set that would be used to map contour lines in contour maps for landfills. This program simplified and streamlined and extremely tedious task. My boss still uses this program monthly as new data comes in. }
    
\item{}
    {Seven Segment Display Clock}
    {I set up some shift registers to drive a segment display led. There were 6 shift registers driving six segment displays. The shift registers were getting driven by bits from the digital outputs of an Arduino microcontroller. Using the arduino IDE, I was able to pass bits to the shift registers in a way that the segment displays simulated a clock with six outputs, HH:MM:SS}
\end{yearlist}

\section{Software and Hardware skills}

\begin{factlist}

\item{Good level}
     {C++, HTML, CSS, Python, Java, git, gcc, shell,
      MS-DOS, Linux, Diptrace, Multisim, Soldering, Circuit Analysis, Google APIs}

\item{Intermediate}
     {Lua, C, \LaTeX, C#, VHDL, Verilog, PSPICE, Windows Command Line}

\item{Basic level}
     {Objective-C, VBA, POSIX, Mobile Development}

\end{factlist}

\end{document}
